Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-07 response/response.tex

There are other tools that measure the same metrics such as as Kiuwan; or, even 
provide a model to calculate maintainability such as SonarCloud. However, we argue
that BCH is a better tool for the following reasons:

\begin{itemize}
    \item Kiuwan measures 4 guidelines that by name appear to be similar to 
    some of the guidelines measured by BCH: Complexity, Duplicated 
    Code, Size and Coupling\footnote{List available here: \url{https://www.kiuwan.com/docs/display/K5/Metrics}}. 
    However, we did not find the full description of kiuwan's metrics anywhere. Thus, 
    we are ensure that the metrics are the same but we are able to conclude that
    BCH integrates a larger set of metrics.  
    In contrast, 
    SIG provides a full description of the $10$ guidelines/metrics behind better code
    hub plus their relation with maintainability on the book and several scientific papers. 
    \item SonarCloud measures 5 similar metrics to the ones measured by BCH: Complexity, Duplication, 
    Issues, Size and Tests\footnote{List available here: \url{https://sonarcloud.io/documentation/user-guide/metric-definitions/}}. 
    The tool rates maintainability with a letter based on the technical 
    debt ratio which is calculated as the ratio between the cost to develop 
    the software and the cost to fix it. But no information is provided 
    on how the remediation cost and developmet cost are calculated. 
    Better Code Hub contemplates a larger set of maintainability metrics 
    and our formula for maintainability is not only fully explained in our paper but also 
    based on metrics that are fully and publicly described.  
\end{itemize}

We do not know codify and did not find the tool anywhere in static analysis tools 
collections or even through organic search at Google.

We added a Section to 
the paper called \textit{Better Code Hub} where we motivate the Better Code Hub tool and 
compare it with Kiuwan and SonarCloud.

@@

Improving software security is not a trivial task and 
requires implementing patches that might affect software 
maintainability. Our hypothesis is that some of these patches may 
have a negative impact on the software maintainability. With this 
study, we want to understand which maintainability metrics can guide 
security engineers on producing patches with better quality---which 
we evaluate with \textit{\textbf{RQ1: What is the impact of security patches on the
maintainability of open-source software?}}. In this research 
question, we present the results by metric, overall score, severity and programming language
to have a better understanding of the impact of each of these parameters in 
software maintainability.

Different weaknesses may require patches with different characteristics. 
Our hypothesis
is that security patches for different weaknesses can have different 
impacts on software maintainability. Thus, we evaluate this in \textit{\textbf{RQ2: Which weaknesses are more likely to
affect open-source software maintainability?}}. The results can help
security engineers on prioritizing weaknesses and bring awareness to the 
ones that need more attention.

Performing a regular change/refactoring, for instance, to improve the name of 
a variable or function, is different than performing a security patch.
Therefore, we created \textit{\textbf{RQ3: What is the impact of security patches versus 
regular changes on the maintainability of open-source software?}}
to explore if there is a need to pay more attention to 
security patches than regular changes during software maintenance tasks.

The previous information is already included in the paper. However, 
we clarified these points in Section 2, where we present the research questions 
and our hypothesis.

### 2021-02-07 paper/emse20.tex
Better Code Hub section

\subsection{Why Bettter Code Hub?}

SIG---the company behind BCH--has been helping business and technology 
leaders drive their organizational 
objectives by fundamentally improving the health and security of 
their software applications for more than $20$ years. The
inner-working of their SIG-MM model---which is the one behind BCH---was 
scientifically proven~\cite{4335232,5609747,6113040,baggen2012}.
BCH not only considers security on their maintainability model~\cite{6616351}
but also integrates a total of $10$ different code metrics; and, 
code metrics were empirically validated in previous 
work~\cite{Bijlsma:2012:FIR:2317098.2317124,8530041,8919169,8785997}.

As BCH there are other tools that do the same kind of code analysis.
Two examples are Kiuwan and SonarCloud. Kiuwan is not free, their 
inner-workings do not seem to be published anywhere and there is
no clear list of metrics available---we inspected their datasheet.
SonarCloud is free but uses only $4$ of the guidelines (duplication,
size, complexity and code smells) that BCH considers. It also scores 
maintainability. In the following table, we
present a brief comparison between BCH and SonarCloud:

\Sofia{Currently building a script to retrieve the SonarCloud results}

>>>>

\subsection{Bettter Code Hub}

SIG---the company behind BCH---has been helping business and technology 
leaders drive their organizational objectives by fundamentally improving 
the health and security of their software applications for more than $20$ years. 
The inner-workings of their SIG-MM model---the one behind BCH---are 
scientifically proven and certified~\cite{4335232,5609747,6113040,baggen2012}.

BCH checks GitHub codebases against 10 maintainability 
guidelines~\cite{Visser:2016:OREILLY} that were empirically 
validated in previous work~\cite{Bijlsma:2012:FIR:2317098.2317124,8530041,8919169,8785997}.
SIG has devised these guidelines after many years of experience: analyzing more 
than 15 million lines of code every week, SIG maintains the industry’s largest 
benchmark, containing more than 10 billion lines of code across 200+ technologies; SIG 
is the only lab in the world certified by TÜViT to issue ISO 25010 certificates\footnote{Information available here: 
\url{https://www.softwareimprovementgroup.com/methodologies/iso-iec-25010-2011-standard/}}.
BCH's compliance criterion is derived from the requirements for 4-star 
level maintainability (cf. ISO 25010)~\cite{5609747,6113040,baggen2012,Visser:2016:OREILLY}.
SIG performs the threshold calibration
yearly on a proprietary data set to satisfy the requirements of TUViT to
be a certified measurement model.

As BCH there are other tools that also perform code analysis for similar 
metrics. Two examples are Kiuwan and SonarCloud. However, Kiuwan does
not provide the full description of the metrics it measures; and, SonarCloud
although it provides a way of rating software maintainability, the variables 
description of their formula are not available. Both analyze less maintainability
guidelines than BCH and do not have their inner-workings fully and publicly described.
